### 2012-10-30 paper_draft.tex
Fixed two tiny typos, good to go from my end

There are substantial differences in terms of motivation, tested by Tukey's HSD test, between those people who have already been genotyped 
and those who are not planning on getting genotyped. The first group is likely to agree more strongly, on a five-point scale, with motivations for sharing genotypic information. On the other hand, those people who are not planning on getting genotyped are more likely to agree with the following motivations 
for not sharing their data, see table \ref{tab:motivations1}.

@@

\subsection*{Sharing genotypic information}
Currently users can upload their genotyping results from the companies \textit{23andMe}, \textit{deCODEme }and \textit{FamilyTreeDNA} via a web interface to the openSNP 
project. There is experimental support for uploading exomes in the VCF format \cite{Danecek01082011}, as \textit{23andMe} recently started exome sequencing for its customers. So far only the SNPs of the exome data sets are visualized on openSNP, but the downloads include all variation found in the exome.
The uploaded data is published under the Creative Commons Zero license, 
which - in accordance with the Panton Principles \cite{10.1371/journal.pbio.1001195} - 
allows a complete re-use of the data without any constraints.
Between the start of openSNP on 09/27/2011 and 10/27/2012, 633 people have signed 
up with openSNP, and 270 genetic datasets have been made available. The openSNP 
database lists 215,546,685 genotypes which are distributed over 2,140,643 unique SNPs.
Figures \ref{Figure1_label} and \ref{Figure2_label} depict the increase in users and genotyping files over time.

@@

%The advent of DTC genetic testing has led to new ethical and social issues. 
Much of the criticism of DTC genetic testing focusses on the practice 
of delivering medical information without consulting a physician or genetic counsellor to help patients/customers make sense of the information 
and to put the new knowledge to good use \cite{Hauskeller2011,Hogarth2008,Wasson2009}.

>>>>

There are substantial differences in terms of motivation, tested by Tukey's HSD test, between those people who have already been genotyped 
and those who are not planning on getting genotyped. The first group is likely to agree more strongly, on a five-point scale, with motivations for sharing genotypic information. On the other hand, those people who are not planning on getting genotyped are more likely to agree with the several motivations 
for not sharing their data (for an overview of these motivations, see table \ref{tab:motivations1}).

@@

\subsection*{Sharing genotypic information}
Currently users can upload their genotyping results from the companies \textit{23andMe}, \textit{deCODEme }and \textit{FamilyTreeDNA} via a web interface to the openSNP 
project. There is experimental support for uploading exomes in the VCF format \cite{Danecek01082011}, as \textit{23andMe} recently started exome sequencing for its customers. So far only the SNPs of the exome data sets are visualized on openSNP, but the downloads include all variation found in the exome.
The uploaded data is published under the Creative Commons Zero license, 
which - in accordance with the Panton Principles \cite{10.1371/journal.pbio.1001195} - 
allows a complete re-use of the data without any constraints.
Between the start of openSNP on 09/27/2011 and 10/27/2012, 633 people have signed 
up with openSNP, and 270 genetic datasets have been made available. The openSNP 
database lists 215,546,685 genotypes which are distributed over 2,140,643 unique SNPs.
Figures \ref{Figure1_label} and \ref{Figure2_label} depict the increase in users and genotyping files since September 2011.

@@

%The advent of DTC genetic testing has led to new ethical and social issues. 
Much of the criticism of DTC genetic testing focuses on the practice 
of delivering medical information without consulting a physician or genetic counselor to help patients/customers make sense of the information 
and to put the new knowledge to good use \cite{Hauskeller2011,Hogarth2008,Wasson2009}.
